Results

### 2018-03-20 02_analysis.Rmd
Use actual full models

# Interaction models with extra controls
m_amount_c_full <- update(m_amount_c, . ~ . + 
                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_amount_ci_full <- update(m_amount_ci, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_amount_cif_full <-update(m_amount_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
```

@@

# Interaction models with extra controls
m_likely_c_full <- update(m_likely_c, . ~ . + 
                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_likely_ci_full <- update(m_likely_ci, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)

m_likely_cif_full <-update(m_likely_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin)
```

```{r tbl-models-likely, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```

>>>>

# Interaction models with extra controls
m_amount_c_full <- update(m_amount_c, . ~ . + 
                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                            give_charity_3 + volunteer + political_knowledge_bin +
                            ideology_bin + education_bin + religiosity_bin +
                            income_bin + age_bin)

m_amount_ci_full <- update(m_amount_ci, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)

m_amount_cif_full <-update(m_amount_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)
```

@@

# Interaction models with extra controls
m_likely_c_full <- update(m_likely_c, . ~ . + 
                            favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                            give_charity_3 + volunteer + political_knowledge_bin +
                            ideology_bin + education_bin + religiosity_bin +
                            income_bin + age_bin)

m_likely_ci_full <- update(m_likely_ci, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)

m_likely_cif_full <-update(m_likely_cif, . ~ . + 
                             favor_humanitarian_bin + favor_human_rights_bin + favor_development_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)
```

```{r tbl-models-likely, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  quick_docx()
  print_hux()
```
